Causal Inference in Machine Learning: A Review

### 2015-01-15 wiml_poster/a4version.tex
adds final version of WIML poster and first draft of observe approach bandit in simplest setting

\documentclass[b0,landscape,25pt]{sciposter}

\usepackage{multicol,caption} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster

\usepackage[svgnames]{xcolor} % Specify colors by their 'svgnames', for a full list of all colors available see here: http://www.latextemplates.com/svgnames-colors

@@

%\usepackage[boxruled]{algorithm2e}
%\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage[noend]{algpseudocode}% http://ctan.org/pkg/algorithmicx
\newtheorem{Def}{Definition}
\newtheorem{Theorem}{Theorem}

@@

\begin{document}
\def\ci{\perp\!\!\!\perp}
%----------------------------------------------------------------------------------------
%	POSTER HEADER 
%----------------------------------------------------------------------------------------

% The header is divided into three boxes:
% The first is 55% wide and houses the title, subtitle, names and university/organization
% The second is 25% wide and houses contact information
% The third is 19% wide and houses a logo for your university/organization or a photo of you
% The widths of these boxes can be easily edited to accommodate your content as you see fit
\begin{minipage}[t]{0.15\linewidth}%
\centering
\includegraphics[height=12cm]{nicta_logo2.jpg} % Logo or a photo of you, adjust its dimensions here
\end{minipage}
\begin{minipage}[b]{0.65\linewidth}
\centering
\resizebox{\linewidth}{!}{\veryHuge \color{NavyBlue} \textbf{Causal Inference in Machine Learning: A review}}
 \color{Black}\\

\huge \textbf{Finnian Lattimore}\\ % Author(s)
\huge Australian National University\\ % University/organization
finnlattimore@gmail.com

\end{minipage}
\begin{minipage}[t]{0.15\linewidth}
\centering
\includegraphics[height=12cm]{anu-logo-notext}
\end{minipage}

@@

\begin{multicols}{5} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more

@@

\fbox{\begin{minipage}{0.99\columnwidth}%
\textbf{The Three Rules}
\begin{enumerate}
\item A causal DAG remains a causal DAG after an intervention so d-separation still applies.
\begin{equation*}
\label{eq:Do1}
\begin{aligned}
\text{if }  (\boldsymbol{Y} \ci & \boldsymbol{W}|\boldsymbol{X})  \text{ in } G_{\overline{\boldsymbol{X}}}  \\
& P(\boldsymbol{Y}|do(\boldsymbol{X}=\boldsymbol{x}),\boldsymbol{W}=\boldsymbol{w}) = P(\boldsymbol{Y}|do(\boldsymbol{X}=\boldsymbol{x})) 
\end{aligned}
\end{equation*}
\item If $\boldsymbol{Y}$ is independent of \textit{how} variables $\boldsymbol{X}$ take their values then the effect on $\boldsymbol{Y}$ of setting $\boldsymbol{X}$ to some value is equivalent to observing it take that value. If this rule is satisfied the corresponding ignoreability assumption in the counterfactual framework is satisfied.
\begin{equation*}
\label{eq:Do2}
\begin{aligned}
\text{if } (\boldsymbol{Y} \ci  \boldsymbol{\hat{X}}|\boldsymbol{X},\boldsymbol{Z}) & \text{ in } G^{\dagger}\\
& P(\boldsymbol{Y}|do(\boldsymbol{X}=\boldsymbol{x}),\boldsymbol{Z}) = P(\boldsymbol{Y}|\boldsymbol{X}=\boldsymbol{x},\boldsymbol{Z})
\end{aligned}
\end{equation*}
\item If there is no direct causal path from $\boldsymbol{X}$ to $\boldsymbol{Y}$ then intervention on $\boldsymbol{X}$ does not change the distribution of $\boldsymbol{Y}$.
\begin{equation*}
\label{eq:Do2}
\begin{aligned}
\text{if }  (\boldsymbol{Y} \ci  \boldsymbol{\hat{X}}|\boldsymbol{Z}) & \text{ in } G^{\dagger}\\
& P(\boldsymbol{Y}|do(\boldsymbol{X}=\boldsymbol{x}),\boldsymbol{Z}) = P(\boldsymbol{Y}|\boldsymbol{Z})
\end{aligned}
\end{equation*}
\end{enumerate}
\footnotesize (For readability, this is a simplified version of the do-calculus that covers interventions on a single variable or cases where it is sufficient for identifiability to consider intervention on all variables together. The fully general version is only slightly more complex see \cite{Pearl2000})
\normalsize
\end{minipage}}

\columnbreak
\section*{Causal Discovery}

@@

\begin{figure}
\caption{The SGS Algorithm}
\label{fig:SGS}
\centering
{\resizebox{0.45\columnwidth}{!}{\includegraphics{SGS_figure-crop}}}
\end{figure}

@@

\end{multicols}
\end{document}

>>>>

%\documentclass[a4,portrait,25pt]{sciposter}
%\documentclass{article}
\documentclass[20pt]{extreport}

%\usepackage{multicol,caption} % This is so we can have multiple columns of text side-by-side
%\columnsep=100pt % This is the amount of white space between the columns in the poster
%\columnseprule=3pt % This is the thickness of the black line between the columns in the poster
\usepackage[margin=0.3in]{geometry}
\usepackage[svgnames]{xcolor} % Specify colors by their 'svgnames', for a full list of all colors available see here: http://www.latextemplates.com/svgnames-colors

@@

%\usepackage[boxruled]{algorithm2e}
%\usepackage{algorithm}% http://ctan.org/pkg/algorithm
\usepackage[noend]{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{algorithm}% http://ctan.org/pkg/algorithms

\newtheorem{Def}{Definition}
\newtheorem{Theorem}{Theorem}

@@

\title{Causal Inference in Machine Learning: A Review}
\author{Finnian Lattimore\\ Australian National University\\finnlattimore@gmail.com\\\textbf{Apologies,}\\ \textbf{the poster is in Air Canada's lost baggage area} }

\begin{document}
\def\ci{\perp\!\!\!\perp}
\maketitle
%----------------------------------------------------------------------------------------
%	POSTER HEADER 
%----------------------------------------------------------------------------------------

% The header is divided into three boxes:
% The first is 55% wide and houses the title, subtitle, names and university/organization
% The second is 25% wide and houses contact information
% The third is 19% wide and houses a logo for your university/organization or a photo of you
% The widths of these boxes can be easily edited to accommodate your content as you see fit
%\begin{minipage}[t]{0.15\linewidth}%
%\centering
%\includegraphics[height=12cm]{nicta_logo2.jpg} % Logo or a photo of you, adjust its dimensions here
%\end{minipage}
%\begin{minipage}[b]{0.65\linewidth}
%\centering
%\resizebox{\linewidth}{!}{\veryHuge \color{NavyBlue} \textbf{Causal Inference in Machine Learning: %A review}}
% \color{Black}\\

%\huge \textbf{Finnian Lattimore}\\ % Author(s)
%\huge Australian National University\\ % University/organization
%finnlattimore@gmail.com

%\end{minipage}
%\begin{minipage}[t]{0.15\linewidth}
%\centering
%\includegraphics[height=12cm]{anu-logo-notext}
%\end{minipage}

@@

%\begin{multicols}{2} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more

@@

\begin{center} 
\fbox{\begin{minipage}{0.9\textwidth}%
\textbf{The Three Rules}
\begin{enumerate}
\item A causal DAG remains a causal DAG after an intervention so d-separation still applies.
\begin{equation*}
\label{eq:Do1}
\begin{aligned}
& \text{if }  (\boldsymbol{Y} \ci  \boldsymbol{W}|\boldsymbol{X})  \text{ in } G_{\overline{\boldsymbol{X}}}  \\
& P(\boldsymbol{Y}|do(\boldsymbol{X}=\boldsymbol{x}),\boldsymbol{W}=\boldsymbol{w}) = P(\boldsymbol{Y}|do(\boldsymbol{X}=\boldsymbol{x})) 
\end{aligned}
\end{equation*}
\item If $\boldsymbol{Y}$ is independent of \textit{how} variables $\boldsymbol{X}$ take their values then the effect on $\boldsymbol{Y}$ of setting $\boldsymbol{X}$ to some value is equivalent to observing it take that value. If this rule is satisfied the corresponding ignoreability assumption in the counterfactual framework is satisfied.
\begin{equation*}
\label{eq:Do2}
\begin{aligned}
& \text{if } (\boldsymbol{Y} \ci  \boldsymbol{\hat{X}}|\boldsymbol{X},\boldsymbol{Z})  \text{ in } G^{\dagger}\\
& P(\boldsymbol{Y}|do(\boldsymbol{X}=\boldsymbol{x}),\boldsymbol{Z}) = P(\boldsymbol{Y}|\boldsymbol{X}=\boldsymbol{x},\boldsymbol{Z})
\end{aligned}
\end{equation*}
\item If there is no direct causal path from $\boldsymbol{X}$ to $\boldsymbol{Y}$ then intervention on $\boldsymbol{X}$ does not change the distribution of $\boldsymbol{Y}$.
\begin{equation*}
\label{eq:Do2}
\begin{aligned}
&\text{if }  (\boldsymbol{Y} \ci  \boldsymbol{\hat{X}}|\boldsymbol{Z})  \text{ in } G^{\dagger}\\
& P(\boldsymbol{Y}|do(\boldsymbol{X}=\boldsymbol{x}),\boldsymbol{Z}) = P(\boldsymbol{Y}|\boldsymbol{Z})
\end{aligned}
\end{equation*}
\end{enumerate}
\footnotesize (For readability, this is a simplified version of the do-calculus that covers interventions on a single variable or cases where it is sufficient for identifiability to consider intervention on all variables together. The fully general version is only slightly more complex see \cite{Pearl2000})
\normalsize
\end{minipage}}
\end{center}

%\columnbreak
\section*{Causal Discovery}

@@

\begin{figure}
\caption{The SGS Algorithm}
\label{fig:SGS}
\centering
{\resizebox{0.55\columnwidth}{!}{\includegraphics{SGS_figure-crop}}}
\end{figure}

@@

%\end{multicols}
\end{document}
